---
title: "CMS Fast Facts"
subtitle: "April 2026 Release"
logo: assets/CMS_logo_reverse.png
format: 
  dashboard:
    fig-format: png
    theme:
      - cosmo
      - assets/ff_format.scss
    css: assets/print.css
    nav-buttons:
      - icon: github
        href: "#"
        aria-label: "Source Code"
    scrolling: false
knitr:
  opts_chunk: 
    dev: ragg_png
    dpi: 192
resources:
  - assets/CMS_logo_reverse.png
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: dependencies
#| include: false

#dependencies
library(tidyverse)
library(scales, warn.conflicts = FALSE)
library(systemfonts, warn.conflicts = FALSE)
library(patchwork)
library(ggtext)
library(ggrepel)
library(waffle)
library(gt, warn.conflicts = FALSE)
library(gtExtras)

#add colors

source("Scripts/98_color_system.R")

# Register the OTF font used for pictograms
register_font(
  name  = "FontAwesome7Solid",
  plain = "/Users/c0xu/Library/Fonts/Font Awesome 7 Free-Solid-900.otf"
)

```

```{r}
#| label: load_data
#| include: false

#load each dataset needed for each tab, stored in a list element
files <- list.files("Dataout", ".rds") |> str_remove(".rds")
walk(
  files,
  ~ assign(.x, read_rds(paste0("Dataout/", .x, ".rds")), envir = .GlobalEnv)
)
```

# Health Spending

## Row {height="25%"}

:::{.valuebox .text-white  label = "ban_nhe" icon="heart-pulse-fill" color="#4A8C6F"}
National Health Expenditures (NHE)

`r context$bans[["nhe_total"]]`

`r context$years[["nhe_yr"]]`

:::

:::{.valuebox .text-white label = "ban_health-insurance" icon="shield-plus" color="#6E6E6E"}
National Health Insurance Expenditures

`r context$bans[["health_insurance"]]`

`r context$years[["nhe_yr"]]`

:::

:::{.valuebox .text-white label = "ban_fed_spend" icon="bank" color="#015390"}
CMS Federal Program Spending

`r context$bans[["fed_spend"]]`

`r context$years[["fed_spend_yr"]]`

:::

## Row

### Column

#### Row {height="40%"}
```{r}
#| label: share-gdp
#| title: "NHE share of GDP"

v_nhe_share <- context[["df_nhe_gdp_share"]] |>
  filter(category == "National Health Expenditures") |>
  pull(value_fmt)

context[["df_nhe_gdp_share"]] |>
  ggplot(aes(fill = fill_color, values = value * 100)) +
  geom_waffle(
    n_rows  = 10,       # 10x10 grid = 100 squares
    size    = 1,      # border between squares
    colour  = "white",  # border colour
    flip    = TRUE      # fill column-by-column (bottom to top)
  ) +
  scale_fill_identity() +
  labs(title = v_nhe_share) +
  coord_equal() +
  theme_void(base_family = "Source Sans 3", base_size = 13) +
  theme(
    plot.title =
      element_text(
        size = 70, hjust = .5,
        family = "Source Sans 3", face = "bold",
        color = ff_colors$scales$steel["900"]
      ),
    plot.subtitle = element_text(size = 24, hjust = 0.5, color = "gray40"),
    plot.margin = margin(0, 0, 0, 0)
  )


```

```{r}
#| label: per_capita
#| title: "NHE per capita"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 8
#| fig-height: 4

# Value and scale
n_units <- context[["df_nhe_pc"]]$n_icons

icons <- tibble(
  index = 1:(n_units),
  x     = ((index - 1) %% 5) + 1,
  y     = -((index - 1) %/% 5)
)

icons |>
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf0d6",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 22,
    color  = ff_colors$base[["green"]]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(title = context$df_nhe_pc[["value_fmt"]]) +
  theme_void(base_family = "Source Sans 3") +
  theme(
    plot.title    =
      element_text(
        color = ff_colors$scales$steel["900"],
        face = "bold",
        size = 60,
        hjust = 0.5
      ),
    plot.subtitle = element_text(size = 30, hjust = 0.5, color = "gray40"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```

#### Row

```{r}
#| label: nhe_sources
#| title: "NHE by Source of Funds"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 12

context[["df_nhe_sources"]] |> 
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col() +
  geom_text(
    aes(label = value_format),
    hjust = -.1,
    family = "Source Sans 3",
    size = 18,
    color = ff_colors$elements[["annotation"]]
  ) +
  labs(x = NULL, y = NULL) +
  scale_fill_identity() +
  scale_x_continuous(expand = c(.001, .001)) +
  coord_cartesian(clip = "off") +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
    strip.text =
      element_text(
        family = "Source Sans 3 SemiBold",
        color = ff_colors$scales$steel[["900"]],
        size = 50,
        hjust = 0
      )
  )

```

### Column

```{r}
#| label: insurance_bar
#| title: "National Health Insurance Expenditures by Payer"
#| fig-height: 8
#| out.height: "100%"
#| fig-width: 6

context[["df_insurance"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.3)) +
  geom_col() +
  geom_text(
    aes(label = value_fmt),
    hjust = -.2, size = 6,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_wrap(
    ~fct_reorder(sub_category, value, .desc = TRUE),
    ncol = 1, scales = "free_y"
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    strip.text =
      element_text(
        family = "Source Sans 3 SemiBold",
        color = ff_colors$scales$steel[["900"]],
        size = 20, hjust = 0
      ),
    panel.spacing = unit(0, "lines"),
    panel.grid = element_blank()
  )
```

### Column

#### Row {height="60%"}
```{r}
#| label: fed_spend_pictogram
#| title: "CMS Spending by Category"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 12

context[["df_spend"]] |>
  ggplot(aes(value, sub_category, fill = fill_color)) +
  geom_blank(aes(value * 1.2)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  facet_wrap(
    ~fct_rev(category), ncol = 1,
    scales = "free_y", space = "free_y"
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
    strip.text =
      element_text(
        family = "Source Sans 3 SemiBold",
        color = ff_colors$scales$steel[["900"]],
        size = 50,
        hjust = 0
      )
  )
```


#### Row {height="40%"}
```{r}
#| label: fte
#| title: "CMS Full-Time Equivalents (FTEs)"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

n_units <- context[["fte"]]$n_icons

icons <- tibble(
  x     = 1:(n_units),
  y     = 0
)

icons |>
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf007",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 50,
    color  = "#015390" #ff_colors$scales$steel["900"]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(title    = context$fte[["value_fmt"]]) +
  theme_void(base_family = "Source Sans 3") +
  theme(
    plot.title =
      element_text(
        size = 80,
        hjust = .5,
        face = "bold",
        color = ff_colors$scales$steel["900"]
      ),
    plot.subtitle = element_text(size = 30, hjust = 0.5, color = "gray40"),
    plot.caption  = element_text(size = 9, hjust = 0.5, color = "gray60"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```


## Row {.no-title height="5%"}

::: {.footer-source}
`r context[["footnote"]]`
:::


# Beneficiary Enrollment


## Row {height="25%"}


:::{.valuebox .text-white label = "ban_medicare_ab" icon="heart-fill" color="#0071BC"}
Total Medicare Beneficiaries

`r enrollment$bans[["medicare_ab"]]`

`r enrollment$years[["medicare"]]`

:::


:::{.valuebox .text-white label = "ban_medicare_d" icon="prescription2" color="#00538C"}
Medicare Part D Beneficiaries

`r enrollment$bans[["medicare_d"]]`

`r enrollment$years[["medicare"]]`

:::

:::{.valuebox .text-white label = "ban_medicaid" icon="people-fill" color="#00A99D"}
Medicaid & CHIP Beneficiaries
 
`r enrollment$bans[["medicaid"]]`

`r enrollment$years[["medicaid"]] |> str_sub(start = -4)`

:::

## Row

### Column

```{r}
#| label: df_medicare_trend
#| title: >-
#|   Medicare Advantage Beneficiaries Now Exceeds
#|    Original Medicare Beneficiaries
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 8

plot_years <- min(enrollment[["df_medicare_trend"]]$data_year):max(enrollment[["df_medicare_trend"]]$data_year)

years_labels <- case_when(
  plot_years == 2008          ~ "2008",
  plot_years == 2025          ~ "'25",
  plot_years %% 2 == 0        ~ paste0("'", str_sub(plot_years, -2)),  
  TRUE                   ~ ""                                 
)

enrollment[["df_medicare_trend"]] |>
  ggplot(aes(x = data_year)) +
  geom_blank(aes(y = value_ma * .9)) +
  geom_blank(aes(y = value_orig * 1.3)) +
  geom_ribbon(
    aes(
      ymin = pmin(value_orig, value_ma),
      ymax = pmax(value_orig, value_ma)
    ),
    fill = ff_colors$base["warmgray"], #"lightgray",
    alpha = 0.3
  ) +
  geom_label(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(data_year == min(data_year)),
    aes(y = value_orig, label = lab_orig, color = "Original Medicare"),
    family = "Source Sans 3", linewidth = NA,
    vjust = -.5, hjust = .6, na.rm = TRUE
  ) +
  geom_label(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(data_year == min(data_year)),
    aes(y = value_ma, label = lab_ma, color = "Medicare Advantage"),
    family = "Source Sans 3", linewidth = NA,
    vjust = 1.1, na.rm = TRUE
  ) +
  geom_label(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(data_year == max(data_year)),
    aes(y = value_orig, label = lab_orig, color = "Original Medicare"),
    family = "Source Sans 3", linewidth = NA,
    vjust = 1, hjust = 0, na.rm = TRUE
  ) +
  geom_label(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(data_year == max(data_year)),
    aes(y = value_ma, label = lab_ma, color = "Medicare Advantage"),
    family = "Source Sans 3", linewidth = NA,
    vjust = -.4, hjust = 0, na.rm = TRUE
  ) +
  geom_line(
    aes(y = value_orig, color = "Original Medicare"), 
    linewidth = 1.5,
    linetype = 'dotted'
  ) +
  geom_line(
    aes(y = value_ma, color = "Medicare Advantage"), 
    linewidth = 1.5,
    linetype = 'dotted'
  ) +
  geom_line(
    aes(y = value_orig, color = "Original Medicare"), linewidth = 2,
    data = enrollment[["df_medicare_trend"]] |> filter(data_year != 2025)
  ) +
  geom_line(
    aes(y = value_ma, color = "Medicare Advantage"), linewidth = 2,
    data = enrollment[["df_medicare_trend"]] |> filter(data_year != 2025)
    ) +
  geom_point(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(
        data_year %in% range(enrollment[["df_medicare_trend"]]$data_year)
      ),
    aes(y = value_orig, color = "Original Medicare")
  ) +
  geom_point(
    data =
      enrollment[["df_medicare_trend"]] |>
      filter(
        data_year %in% range(enrollment[["df_medicare_trend"]]$data_year)
      ),
    aes(y = value_ma, color = "Medicare Advantage")
  ) +
  geom_label(
    aes(y = value_orig, label = lab_orig_cat, color = "Original Medicare"),
    family = "Source Sans 3 SemiBold", linewidth = NA,
    vjust = -.9, hjust = 0, na.rm = TRUE
  ) +
  geom_label(
    aes(y = value_ma, label = lab_ma_cat, color = "Medicare Advantage"),
    family = "Source Sans 3 SemiBold", linewidth = NA,
    vjust = 1.5, hjust = 0, na.rm = TRUE
  ) +
  scale_color_manual(
    values =
      c(
        "Original Medicare" = ff_colors$scales$cobolt[["900"]],
        "Medicare Advantage" = ff_colors$scales$cobolt[["200"]]
      )
  ) +
  scale_y_continuous(
    labels = label_number(scale_cut = cut_short_scale()),
    limits = c(0, NA)
  ) +
  scale_x_continuous(
    limits = c(
      min(enrollment[["df_medicare_trend"]]$data_year),
      max(enrollment[["df_medicare_trend"]]$data_year) + 4
    ),
    breaks = seq(
      from = min(enrollment[["df_medicare_trend"]]$data_year),
      to = max(enrollment[["df_medicare_trend"]]$data_year),
      by = 1
    ),
    labels = years_labels
  ) +
  labs(x = NULL, y = NULL, caption = "Note: CY 2025 values are preliminary") +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    # axis.text.y = element_blank(),
    plot.caption = element_text(size = 14, color = "#909090"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```


### Column

```{r}
#| label: df_disagg_trend
#| title: "Sub-Populations Trends"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 8

v_medicare_subpop <- enrollment[["df_disagg_trend"]] |>
  filter(area == "Medicare") |> 
  ggplot(
    aes(
      data_year, value,
      group = sub_category,
      fill = fill_color, color = fill_color
    )
  ) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .4) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(area ~ fct_reorder2(sub_category, data_year, value), switch = "y") +
  # facet_wrap(~fct_rev(area) + fct_reorder2(sub_category, data_year, value)) +
  scale_x_continuous(
    breaks = range(enrollment[["df_disagg_trend"]]$data_year),
    limits = range(enrollment[["df_disagg_trend"]]$data_year)
  ) +
  scale_color_identity() +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    strip.text =
      element_text(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    strip.placement = "outside",
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

v_mediaid_subpop <- enrollment[["df_disagg_trend"]] |>
  filter(area == "Medicaid & CHIP") |> 
  ggplot(
    aes(
      data_year, value,
      group = sub_category,
      fill = fill_color, color = fill_color
    )
  ) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .4) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(area ~ fct_reorder2(sub_category, data_year, value), switch = "y") +
  # facet_wrap(~fct_rev(area) + fct_reorder2(sub_category, data_year, value)) +
  scale_x_continuous(
    breaks = sort(c(2017, range(enrollment[["df_disagg_trend"]]$data_year))),
    limits = range(enrollment[["df_disagg_trend"]]$data_year)
  ) +
  scale_color_identity() +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    strip.text =
      element_text(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    strip.placement = "outside",
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

((v_medicare_subpop | plot_spacer()) +
  plot_layout(widths = c(2, 1)) ) / v_mediaid_subpop 
```



## Row {.no-title height="5%"}

::: {.footer-source}
`r enrollment[["footnote"]]`
:::

# Utilization

## Row {height="25%"}

:::{.valuebox .text-white label = "ban_medicare_util" icon="heart-fill" color="#0071BC"}
Original Medicare Program Payments/Persons Served

`r utilization$bans[["medicare_total"]]`

`r utilization$year[["medicare_total"]]`

:::


:::{.valuebox .text-white label = "ban_medicare_d_util" icon="prescription2" color="#00538C"}
Medicare Part D Expenditures/Utilizers

`r utilization$bans[["part_d"]]`

`r utilization$year[["part_d"]]`

:::

:::{.valuebox .text-white label = "ban_medicaid_exp" icon="people-fill" color="#00A99D"}
Medicaid Expenditures

`r utilization$bans[["medicaid_chip"]]`

`r utilization$year[["medicaid_chip"]]`


:::

## Row

### Column

```{r}
#| label: orig_medicare_utilization
#| title: Original Medicare Utilization & Spending
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 10

df_background <- utilization[["df_medicare_util"]] |> select(-category)

utilization[["df_medicare_util"]] |>
  ggplot(aes(persons_served, payments, fill = category)) +
  # geom_point(
  #   data = df_background,
  #   aes(persons_served, payments),
  #   fill = "grey80", color = "white",
  #   shape = 21,
  #   size = 5,
  #   inherit.aes = FALSE
  # ) +
  geom_point(shape = 21, color = "white", size = 7) +
  geom_point(
    data =
      utilization[["df_medicare_util"]] |> filter(sub_category == "Total"),
    shape = 23, color = "white", size = 8
  ) +
  geom_text_repel(
    aes(label = sub_category),
    point.padding = 3,
    box.padding = .5,
    min.segment.length = 0,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    size = 8
  ) +
  facet_wrap(~category) +
  scale_fill_manual(
    values = c(
      ff_colors$scales$cobolt[["200"]],
      ff_colors$scales$cobolt[["700"]],
      ff_colors$scales$cobolt[["900"]]
    )
  ) +
  scale_x_continuous(labels = label_number(scale_cut = cut_short_scale())) +
  scale_y_continuous(
    labels = label_number(prefix = "$", scale_cut = cut_short_scale())
  ) +
  labs(x = "Persons Served", y = "Program Payments", color = "", shape = "") +
  theme_minimal(base_size = 22, base_family = "Source Sans 3") +
  theme(
    panel.spacing = unit(2, "lines"),
    legend.position = "none",
    strip.text =
      element_text(
        color = ff_colors$elements[["title"]],
        face = "bold",
        size = 18
      ),
    axis.title = element_text(face = "bold"),
  )
```

### Column

#### Row

```{r}
#| label: part_d
#| title: Part D Utilization & Expenditures
#| out-width: 100%
#| out-height: 100%

utilization[["df_part_d"]] |>  
  gt(groupname_col = "group", rowname_col = "sub_category") |> 
  cols_align(align = "right", columns = "latest_value_lab") |> 
  cols_align(align = "right", columns = "sub_category") |> 
  cols_label(
    latest_value_lab = utilization[['part_d_year']],
    value = 
      str_glue(
        "Last {utilization[['part_d_duration']]} Years Trend"
        )
  ) |> 
  gt_plt_sparkline(
    value, 
    palette = c(ff_colors$scales$cobolt["700"], rep("transparent", 4)),
    same_limit = FALSE,
    label = FALSE
  ) |> 
  opt_table_font(font = "Source Sans 3") |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
)

```

#### Row

```{r}
#| label: medicaid_exp
#| title: Medicaid Expenditures
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 8

utilization[["df_medicaid_exp"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value))) +
  geom_blank(aes(x = value * 1.3)) +
  geom_col(fill = ff_colors$base[["teal"]]) +
  geom_text(
    aes(label = value_fmt),
    hjust = -.1, family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    size = 12
  ) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(expand = c(.005, .005)) +
  labs(
    x = NULL, y = NULL
  ) +
  theme_minimal(base_size = 35) +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title =
      element_text(
        face = "bold",
        color = ff_colors$elements[["title"]]
      )
  )
```

## Row {.no-title height="5%"}

::: {.footer-source}
`r enrollment[["footnote"]]`
:::


# Cost Sharing


## Row {height="95%"}

### Column


```{r}
#| label: premiums
#| title: "Premiums"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 6

cost_sharing[["df_cs_trend"]] |> 
  filter(metric_lab == "Premiums") |> 
  ggplot(aes(data_year, value, group = ln_group, fill = fill_color, color = fill_color)) +
  geom_blank(aes(y = value * 1.1)) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .2) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(~sub_category) +
  scale_x_continuous(
    breaks =
      range(
        unique(cost_sharing[["df_cs_trend"]]$data_year),
        na.rm = TRUE
      )
  ) +
  scale_fill_identity() + 
  scale_color_identity() + 
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Source Sans 3", base_size = 28) +
  theme(
    legend.position = "none",
    strip.text =
      element_markdown(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

```


```{r}
#| label: deductibles
#| title: "Deductibles"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 6

cost_sharing[["df_cs_trend"]] |> 
  filter(metric_lab == "Deductibles") |> 
  ggplot(aes(data_year, value, group = ln_group, fill = fill_color, color = fill_color)) +
  geom_blank(aes(y = value * 1.1)) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .2) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(~sub_category) +
  scale_x_continuous(
    breaks =
      range(
        unique(cost_sharing[["df_cs_trend"]]$data_year),
        na.rm = TRUE
      )
  ) +
  scale_fill_identity() + 
  scale_color_identity() + 
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Source Sans 3", base_size = 28) +
  theme(
    legend.position = "none",
    strip.text =
      element_markdown(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

```

### Column


```{r}
#| label: coinsurance
#| title: "Coinsurance (Part A)"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 6

cost_sharing[["df_cs_trend"]] |> 
  filter(metric_lab == "Part A Coinsurance") |> 
  ggplot(aes(data_year, value, group = ln_group, fill = fill_color, color = fill_color)) +
  geom_blank(aes(y = value * 1.1)) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .2) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(~sub_category) +
  scale_x_continuous(
    breaks =
      range(
        unique(cost_sharing[["df_cs_trend"]]$data_year),
        na.rm = TRUE
      )
  ) +
  scale_fill_identity() + 
  scale_color_identity() + 
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Source Sans 3", base_size = 28) +
  theme(
    legend.position = "none",
    strip.text =
      element_markdown(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

```

```{r}
#| label: other_part_d
#| title: "Part D Out-of-Pocket Threshold"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 6

v_outofpocket <- cost_sharing[["df_cs_trend"]] |> 
  filter(metric_lab == "Part D Out-of-Pocket Threshold") |> 
  ggplot(aes(data_year, value, group = ln_group, fill = fill_color, color = fill_color)) +
  geom_blank(aes(y = value * 1.1)) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .2) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(~sub_category) +
  scale_x_continuous(
    breaks =
      range(
        unique(cost_sharing[["df_cs_trend"]]$data_year),
        na.rm = TRUE
      )
  ) +
  scale_fill_identity() + 
  scale_color_identity() + 
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Source Sans 3", base_size = 28) +
  theme(
    legend.position = "none",
    strip.text =
      element_markdown(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )

v_outofpocket + plot_spacer() + plot_spacer()

```

## Row {.no-title height="5%"}

::: {.footer-source}
`r cost_sharing[["footnote"]]`
:::

# Providers

## Row {height="25%"}

:::{.valuebox .text-white label = "ban_non_inst" icon="clipboard2-pulse-fill" color="#00538C"}
Medicare Non-Institutional Providers

`r providers$bans[["Non-Institutional"]]`

`r providers$years["Non-Institutional"]`

:::

:::{.valuebox .text-white label = "ban_Labs" icon="flask" color="#858585"}
Medicare Lab Providers

`r providers$bans[["Lab"]]`

`r providers$years["Lab"]`

:::

:::{.valuebox .text-white label = "ban_DMEPOS" icon="people-fill" color="#0071BC"}
Medicare DMEPOS Providers

`r providers$bans[["DMEPOS"]]`

`r providers$years["DMEPOS"]`

:::

:::{.valuebox .text-white label = "ban_inst" icon="hospital" color="#59A8DC"}
Medicare Institutional Providers

`r providers$bans[["Institutional"]]`

`r providers$years["Institutional"]`

:::


## Row

### Column

```{r}
#| label: noninstitutional_providers
#| title: Non-Institutional Provider Types
#| out-width: 100%
#| out-height: 100%
#| fig-width: 20
#| fig-height: 20

providers[["df_provider_noninst"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y =
      element_text(
        # color = ff_colors$elements[["axis"]],
        size = 40
      ),
  )

```

### Column

```{r}
#| label: dmepos_viz
#| title: DMEPOS Provider Types
#| out-width: 100%
#| out-height: 100%
#| fig-width: 20
#| fig-height: 20

providers[["df_providers_dmepos"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.3
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 40)
  )
```

### Column

#### Row {height="60%"}
```{r}
#| label: institutional_providers
#| title: Institutional Provider Types
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 10

providers[["df_provider_inst"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
  )
```


#### Row {height="40%"}

```{r}
#| label: hopsital_type
#| title: Hospital Provider Subset
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 6

providers[["df_hospital_subset"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
  )

```


## Row {.no-title height="5%"}

::: {.footer-source}
`r providers[["footnote"]]`
:::

# Notes

## Row 

### Column

::: {.card}

# Health Spending 

  - Total Medicaid Amount reported as total gross outlays including the Vaccines for Children Program.

# Enrollment

  - Populations may not add due to rounding
  - Medicare Advantage (MA) total includes both MA and other health plan enrollment
  - Medicare CY2025 and Medicaid & CHIP  data points are preliminary and subject to change 
  - Medicaid & CHIP 
      - Total count represent the number of Medicaid and CHIP beneficiaries with comprehensive coverage.  The categories are sourced from data that include beneficiaries with non-comprehensive coverage and do not sum to the total counts.
      - Dual Eligible includes Aged, Disabled & ESRD; Counts represent full-benefit eligible individuals.
      - 2025 data not yet available for Dual Eligible and Medicaid Expansion Adults


# Utilization

  - Medicaid & CHIP 
      - Payments for All Services includes payments for additional services not broken out separately.
      - Fee-for-service payments = (a) Inpatient Services, (b) Long-Term Care, (c) Physician, Laboratory, and Other Services, and (d) Prescription Drugs
      - Expenditures by service category do not sum to the total expenditures.  Total expenditures also include Medicare payments for some beneficiaries and adjustments to prior year payments.  Managed care expenditures cover the same services that are delivered via fee-for-service.  Data do not permit allocation of managed care expenditures to the different service categories.  These expenditures are from all Medicaid beneficiaries, regardless of eligibility. 
  - The Medicaid & CHIP population and expenditure data are from the [Medicaid & CHIP scorecard](https://www.medicaid.gov/state-overviews/scorecard/who-enrolls-medicaid-chip/index.html)
:::

### Column

::: {.card}

# Cost Sharing

  - The inpatient hospital deductible applies per benefit period.  
  - For Part D, the initial coverage limit was eliminated in 2025. More information can be found [here](https://www.cms.gov/files/document/final-cy-2025-part-d-redesign-program-instructions.pdf)
  
# Providers

  - In historic Fast Facts files, Labs are categorized as Institutional Providers, but can in fact call under any category. As such, they have been seperated out here so as not to add into the total for Institutional Providers.
  - Non-Institutional Proviers - Providers utilized by Original Medicare beneficiaries for all Part B non-institutional/DMEPOS provider services.  Providers may be counted in more than one specialty classification but are reported as a single provider in the "Total Providers" count.

# Abbreviations

  - CHIP - Children's Health Insurance Program
  - DMEPOS - Medicare Durable Medical Equipment, Prosthetics, Orthotics and Supplies
  - LTR - Life Time Reserve
  - MA - Medicare Advantage
  - MAPD - Medicare Advantage Prescription Drug Plan
  - PDP - Prescription Drug Plan
  - PT - Physical Therapy
  - SNF - Skilled Nursing Facility

:::

## Row {.no-title height="5%"}

::: {.footer-source}
`r providers[["footnote"]]`
:::
