---
title: "CMS Fast Facts"
subtitle: "April 2025 Release"
logo: assets/CMS_logo_reverse.png
format: 
  dashboard:
    fig-format: png
    theme:
      - cosmo
      - assets/ff_format.scss
    nav-buttons:
      - icon: github
        href: "#"
        aria-label: "Source Code"
    scrolling: false
    dpi: 330
knitr:
  opts_chunk: 
    dev: ragg_png
resources:
  - assets/CMS_logo_reverse.png
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: dependencies
#| include: false

#dependencies
library(tidyverse)
library(scales, warn.conflicts = FALSE)
library(systemfonts, warn.conflicts = FALSE)
library(ggrepel)
library(waffle)
library(gt, warn.conflicts = FALSE)
library(gtExtras)

#add colors

source("Scripts/98_color_system.R")

# Register the OTF font used for pictograms
register_font(
  name  = "FontAwesome7Solid",
  plain = "/Users/c0xu/Library/Fonts/Font Awesome 7 Free-Solid-900.otf"
)

# register_variant(
#   "Source Sans 3 Black",
#   family = "Source Sans 3",
#   weight = "heavy"
# )

```

```{r}
#| label: load_data
#| include: false

#load each dataset needed for each tab, stored in a list element
files <- list.files("Dataout", ".rds") |> str_remove(".rds")
walk(
  files,
  ~ assign(.x, read_rds(paste0("Dataout/", .x, ".rds")), envir = .GlobalEnv)
)
```

# Context

## Row {height="95%"}

### Column

#### Row {height="25%"}
:::{.valuebox .text-white  label = "ban_nhe" icon="heart-pulse-fill" color="#015390"}
National Health Expenditures (NHE)

`r context$bans[["nhe_total"]]`

`r context$years[["nhe_yr"]]`

:::

#### Row {height="50%"}
```{r}
#| label: share-gdp
#| title: "NHE share of GDP"
#| out-width: 100%
#| fig-height: 4


context[["df_nhe_gdp_share"]] |> 
  ggplot() +
    geom_rect(
      aes(
        xmin = 0,
        xmax = 12,
        ymin = 0,
        ymax = 100 / 12
      ),
      color =  "#A6A6A6",
      fill = "white", 
      linewidth = 1.1
    ) +
    geom_rect(
      aes(
        xmin = 0,
        xmax = value_sqrt,
        ymin = 0,
        ymax = value_sqrt
      ),
      fill = ff_colors$base[["green"]]
    ) +
    labs(title = context[["df_nhe_gdp_share"]]$value_fmt) +
    coord_equal() +
    theme_void() +
    theme(
      plot.title = element_text(
        size = 30, hjust = .5, 
        family = "Source Sans 3", face = "bold",
        color = ff_colors$scales$steel["900"]
        ),
      plot.margin = margin(0, 0, 0, 0)
      )


```

#### Row {height="25%"}
```{r}
#| label: per_capita
#| title: "NHE per capita"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

# Value and scale
n_units <- context[["df_nhe_pc"]]$n_icons

icons <- tibble(
  index = 1:(n_units),
  x     = index,
  y     = 0
)

icons |> 
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf0d6",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 18,
    color  = ff_colors$base[["green"]]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(
    title    = context$df_nhe_pc[["value_fmt"]],
    subtitle = "Each icon ≈ $1,000"
  ) +
  theme_void() +
  theme(
    plot.title    = element_text(face = "bold", size = 60, hjust = 0.5),
    plot.subtitle = element_text(size = 25, hjust = 0.5, color = "gray40"),
    plot.caption  = element_text(size = 9, hjust = 0.5, color = "gray60"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```

### Column

### Row {height=20%}

:::{.valuebox .text-white label = "ban_health-insurance" icon="shield-plus" color="#015390"}
Health Insurance

`r context$bans[["health_insurance"]]`

`r context$years[["nhe_yr"]]`

:::

:::{.valuebox .text-white label = "ban_health-insurance" icon="shield-plus" color="#015390"}
Health Insurance

`r context$bans[["health_insurance"]]`

`r context$years[["nhe_yr"]]`

:::

#### Row {height=75%}

```{r}
#| label: insurnace_bar
#| title: "Health Expenditures by Payer"
#| fig-height: 8        # Increase this to stretch the plot vertically
#| out.height: "100%"   # Tells the output to fill the container
#| fig-width: 6

context[["df_insurance"]] |> 
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.3)) +
  geom_col() +
  geom_text(
    aes(label = value_fmt),
    hjust = -.2, size = 6, family = "Source Sans 3", color = ff_colors$elements[["annotation"]]
    ) + 
  facet_wrap(~fct_reorder(sub_category, value, .desc = TRUE), ncol = 1, scales = "free_y") +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    strip.text = element_text(
      family = "Source Sans 3",
      color = ff_colors$elements[["annotation"]],
      size = 20, hjust = 0),
    panel.spacing = unit(0, "lines"),
    panel.grid = element_blank()
  )


```

### Column

### Row {height=20%}

:::{.valuebox .text-white label = "ban_fed_spend" icon="bank" color="#015390"}
CMS Federal Program Spending

`r context$bans[["fed_spend"]]`

`r context$years[["fed_spend_yr"]]`

:::

:::{.valuebox .text-white label = "ban_fed_spend" icon="bank" color="#015390"}
CMS Federal Program Spending

`r context$bans[["fed_spend"]]`

`r context$years[["fed_spend_yr"]]`

:::

#### Row

##### Row
```{r}
#| label: fed_spend_pictogram
#| title: "CMS Spending by Category"

context[["df_spend"]] |> 
  filter(category == "Federal Program Spending") |> 
  ggplot(aes(values = squares, fill = fill_color)) +
  geom_waffle(
    n_rows  = 10,
    size    = 1.5,
    colour  = "white",
    flip    = FALSE
  ) +
  scale_fill_identity() +
  labs(
    subtitle = "Each square represents ~1% of total",
    # caption  = "Source: CMS",
    fill     = NULL
  ) +
  coord_fixed() +
  theme_void() +
  theme(
    plot.title    = element_text(face = "bold", size = 30, hjust = 0.5),
    plot.subtitle = element_text(size = 25, hjust = 0.5, color = "gray40"),
    legend.position = "none"
  )
```

##### Row

```{r}
#| label: spend_table

context[["df_spend"]] |> 
  select(fill_color, category, sub_category, value_fmt) |> 
  gt(groupname_col =  "category") |> 
  cols_label(
    fill_color = "",
    sub_category = "",
    value_fmt = "Gross Outlays"
  ) |> 
 text_transform(
    locations = cells_body(columns = fill_color),
    fn = function(x) {
      glue::glue(
        "<span style='display:inline-block; width:14px; height:14px;
         border-radius:3px; background-color:{x};'></span>"
      )
    }
  ) |>
  cols_align(align = "center", columns = fill_color) |>
  cols_align(align = "right", columns = value_fmt) |>
  cols_width(fill_color ~ px(24)) |>
  opt_row_striping(row_striping = FALSE) |> 
  tab_style(
    style = cell_fill(color = "transparent"),  # or "transparent"
    locations = cells_body(rows = everything())
  ) |> 
  tab_options(
    table.border.top.style            = "none",
    table.border.bottom.style         = "none",
    column_labels.border.top.style    = "none",
    column_labels.border.bottom.style = "none",
    data_row.padding                  = px(4),
    container.width = pct(100),
    table.width = pct(100),
    container.height = pct(100),
    container.overflow.y = "hidden"

  )
```


#### Row {height="20%"}
```{r}
#| label: fte
#| title: "CMS Full-Time Equivalents (FTEs)"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

n_units <- context[["fte"]]$n_icons

icons <- tibble(
  x     = 1:(n_units),
  y     = 0
)

icons |> 
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf007",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 30,
    color  = ff_colors$scales$steel["900"]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(
    title    = context$fte[["value_fmt"]],
    subtitle = "Each icon represents ~1,000 FTEs"
  ) +
  theme_void() +
  theme(
    plot.title    = element_text(face = "bold", size = 60, hjust = 0.5),
    plot.subtitle = element_text(size = 25, hjust = 0.5, color = "gray40"),
    plot.caption  = element_text(size = 9, hjust = 0.5, color = "gray60"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```


## Row {.no-title height="5%"}

::: {.footer-source}
CMS Fast Facts April 2025 Release &bull; Data sources: CMS/Office of the Actuary, CMS/Office of Financial Management 
:::

# Beneficiaries

## Row {height=25%}

:::{.valuebox .text-white label = "ban_medicare_ab" icon="heart-fill" color="#015390"}
Medicare Parts A/B

`r beneficiaries$bans[["medicare_ab"]]`

`r beneficiaries$years[["ban_year"]]`

:::


:::{.valuebox .text-white label = "ban_medicare_d" icon="capsule-pill" color="#015390"}
Medicare Part D

`r beneficiaries$bans[["medicare_d"]]`

`r beneficiaries$years[["ban_year"]]`

:::

:::{.valuebox .text-white label = "ban_medicaid" icon="people-fill" color="#015390"}
Medicaid & CHIP

`r beneficiaries$bans[["medicaid"]]`

`r beneficiaries$years[["ban_year"]]`

:::


## Row
```{r}
#| label: df_medicare_trend
#| title: "Medicare Advantage Overtaking Original Medicare"

beneficiaries[["df_medicare_trend"]] |>
  ggplot(aes(x = data_year)) +
  geom_ribbon(
    aes(
      ymin = pmin(original_medicare, ma),
      ymax = pmax(original_medicare, ma)
    ),
    fill = ff_colors$base["warmgray"], #"lightgray",
    alpha = 0.3
  ) +
  geom_line(aes(y = original_medicare, color = "Original Medicare")) +
  geom_line(aes(y = ma, color = "Medicare Advantage")) + 
  geom_point(aes(y = original_medicare, color = "Original Medicare")) +
  geom_point(aes(y = ma, color = "Medicare Advantage")) +
  geom_text(
    aes(y = original_medicare, label = lab_og), 
    family = "Source Sans 3",
    vjust = -1, na.rm = TRUE
    ) +
  geom_text(
    aes(y = ma, label = lab_ma), 
    family = "Source Sans 3", color = ff_colors$elements["annotation"],
    vjust = 1.4, na.rm = TRUE
    ) +
  geom_text(
    aes(y = original_medicare, label = lab_og_cat, color = "Original Medicare"), 
    family = "Source Sans 3",
    vjust = -2.5, hjust = 0, na.rm = TRUE
    ) +
  geom_text(
    aes(y = ma, label = lab_ma_cat, color = "Medicare Advantage"), 
    family = "Source Sans 3",
    vjust = 2.5, hjust = 0, na.rm = TRUE
    ) +
  scale_color_manual(
    values = c(
      "Original Medicare" = ff_colors$scales$cobolt[["900"]],
      "Medicare Advantage" = ff_colors$scales$cobolt[["200"]]
      )
      ) +
  labs(x = NULL, y = NULL) +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.text.y = element_blank()
  )
  
```

```{r}
#| label: df_medicaid_trend
#| title: "Trends in Medicaid Sub-Populations"

beneficiaries[["df_medicaid_trend"]] |> 
  ggplot(aes(data_year, value, group = sub_category, fill = fill_color, color = fill_color)) +
  geom_area(alpha = .4) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val), 
    vjust = -1, na.rm = TRUE, 
    family = "Source Sans 3", 
    color = ff_colors$elements[["annotation"]]
    ) +
  facet_grid(~fct_reorder2(sub_category, data_year, value)) +
  scale_x_continuous(breaks = range(unique(beneficiaries[["df_medicaid_trend"]]$data_year), na.rm = TRUE)) +
  scale_color_identity() +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    strip.text = element_text(
      color = ff_colors$elements[["title"]],
      face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
  )
```

## Row
```{r}
#| label: orig_medicare_utilization
#| title: Medicare Utilization

beneficiaries[["df_medicare_util"]] |> 
  ggplot(aes(metric, zscore, group = sub_category, color = category)) +
  geom_line() +
  geom_point() +
  geom_text(
    aes(label = lab_ben),
    hjust = 1.1,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    na.rm = TRUE
  ) +
  geom_text(
    aes(label = lab_exp),
    hjust = -.2,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    na.rm = TRUE
  ) +
  facet_wrap(~category) +
  scale_color_manual(
    values = 
      c(
        ff_colors$scales$cobolt[["200"]],
        ff_colors$scales$cobolt[["700"]],
        ff_colors$scales$cobolt[["900"]]
      )) +
  labs(x = NULL, y = NULL) +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 22) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "none",
    strip.text = element_text(face = "bold", color = ff_colors$elements[["title"]])
  )

# df_medicare_util |>
#   filter_out(category %in% c("Part A", "Part B")) |>
#   select(-zscore, -starts_with('lab_')) |>
#   pivot_wider(
#     names_from = metric
#   ) |>
#   ggplot(aes(beneficiaries, payments, color = group)) +
#   geom_point() +
#   geom_text(aes(label = category)) +
#   # facet_wrap(~group) +
#   labs(x = "Persons Served (millions)", y = "Payments (billions)") +
#   theme_minimal()
```
```{r}
#| label: medicaid_exp
#| title: Medicaid Expenditures

medicaid_exp_tot <- sum(beneficiaries[['df_medicaid_exp']]$value)

beneficiaries[['df_medicaid_exp']] |> 
  ggplot(aes(value, fct_reorder(sub_category, value))) +
  geom_blank(aes(x = value *1.3)) +
  geom_col(fill = ff_colors$base[["teal"]]) +
  geom_text(
    aes(
      label = value_fmt),
      hjust = -.1, family = "Source Sans 3", color = ff_colors$elements[["annotation"]]
  ) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(expand = c(.005, .005)) +
  labs(
    x = NULL, y = NULL,
    title = str_glue('All Services = {label_comma(1, prefix = "$", cale_cut = cut_short_scale())(medicaid_exp_tot)}')   
  ) +
  theme_minimal(base_size = 22) +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", color = ff_colors$elements[["title"]])
  )
```

# Cost Sharing

## Row {height="20%"}

:::{.valuebox .text-white label = "ban_part_a_benes" icon="people-fill" color="#015390"}
Part A Persons Served

`r cost_sharing$bans[["part_a_persons_served"]]`

`r cost_sharing$years`

:::

:::{.valuebox .text-white label = "ban_part_b_benes" icon="people-fill" color="#015390"}
Part B Persons Served

`r cost_sharing$bans[["part_b_persons_served"]]`

`r cost_sharing$years`

:::

:::{.valuebox .text-white label = "ban_part_d_benes" icon="people-fill" color="#015390"}
Part D Persons Served

`r cost_sharing$bans[["part_d_persons_served"]]`

`r cost_sharing$years`

:::


## Row {height="20%"}

:::{.valuebox .text-white label = "ban_part_a_exp" icon="people-fill" color="#015390"}
Part A Program Payments

`r cost_sharing$bans[["part_a_payments"]]`

`r cost_sharing$years`

:::

:::{.valuebox .text-white label = "ban_part_b_exp" icon="people-fill" color="#015390"}
Part B Program Payments

`r cost_sharing$bans[["part_b_payments"]]`

`r cost_sharing$years`

:::

:::{.valuebox .text-white label = "ban_part_d_exp" icon="people-fill" color="#015390"}
Part D Expenditures

`r cost_sharing$bans[["part_d_payments"]]`

`r cost_sharing$years`

:::

## Row

```{r}
#| label: dumbell_charts
#| title: "Medicare Deductibles, Coinsurance, Premiums"

cost_sharing[["df_cs_trend"]] |> 
  ggplot(aes(value, fct_reorder(sub_category, order, .fun = max, .na_rm = TRUE), group = ln_group)) +
  geom_path(color = ff_colors$scales$cobolt[["200"]], na.rm = TRUE) +
  geom_point(
    color = "white",
    stroke = 1.1, 
    size = 4,
    na.rm = TRUE
  ) +
  geom_point(
    aes(fill = fill_color), na.rm = TRUE,
    shape = 21, 
    color = ff_colors$base[["azure"]], 
    stroke = 1.1, 
    size = 4, alpha = .4) +
  geom_text(
    aes(x = mid_pt, label = delta_lab),
    na.rm = TRUE,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    vjust = -1.1
  ) + 
  # facet_wrap(~group, nrow = 1, scales = "free") +
  facet_wrap(category ~ ., ncol = 1, scales = "free", space = "free_y", strip.position = "top") +
  labs(x = NULL, y = NULL) +
  scale_fill_identity() +
  scale_x_continuous(label = label_currency()) +
  theme_minimal() +
  theme(
    axis.text = element_text(family = "Source Sans 3"),
    strip.text = element_text(family = "Source Sans 3", face = "bold", hjust = 0),
    strip.placement = "outside",
    panel.spacing = unit(0, "lines")
  )
```

# Providers

## Column

### Row {height=20%}

:::{.valuebox .text-white label = "ban_inst" icon="hospital" color="#015390"}
Institutional Providers

`r providers$bans[["Institutional"]]`

`r providers$years["Institutional"]`

:::


### Row

```{r}
#| label: institutional_providers
#| title: "Institutional Providers"

providers[["df_provider_inst"]] |> 
  # ggplot(aes(value, fct_reorder(category, value))) + 
  ggplot(aes(value, category)) + 
  geom_blank(aes(value * 1.1)) +
  geom_col(fill = ff_colors$scales$steel[["700"]]) +
  geom_text(
    aes(label = value_fmt),
    hjust = -.1,
    family = "Source Sans 3", color = ff_colors$elements[['annotation']],
    ) +
  scale_x_continuous(expand = c(.005, .005)) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(family = "Source Sans 3", color = ff_colors$elements[["axis"]]),
    axis.text.x = element_blank()
  )
```

### Row 

#### Column
```{r}
#| label: hopsital_type
#| title: "Hospital Subset"

providers[["df_hospital_subset"]]  |> 
  ggplot(aes(fill = fill_color, values = squares)) +
  geom_waffle(
    n_rows  = 10,
    size    = 1.5,
    colour  = "white",
    flip    = FALSE
  ) +
  scale_fill_identity() +
  labs(
    subtitle = "Each square represents ~1% of total",
    fill     = NULL
  ) +
  coord_fixed() +
  theme_void() +
  theme(
    plot.title    = element_text(face = "bold", size = 30, hjust = 0.5),
    plot.subtitle = element_text(size = 25, hjust = 0.5, color = "gray40"),
    legend.position = "none"
  )
```

#### Column
```{r}
#| label: hopsital_table
#| title: "Hospital Table"

providers[["df_hospital_subset"]]  |> 
  relocate(fill_color, .before = 1) |> 
  arrange(desc(value)) |> 
  select(-squares) |> 
  gt() |> 
  cols_label(
      fill_color = "",
      sub_category = "",
      value = "Count",
      share = "Share"
    ) |> 
  fmt_number(
    columns = value,
    decimals = 0,
    suffixing = FALSE 
    ) |> 
  fmt_percent(
    columns = share,
    decimals = 0
  ) |> 
  text_transform(
    locations = cells_body(columns = fill_color),
    fn = function(x) {
      glue::glue(
        "<span style='display:inline-block; width:14px; height:14px;
         border-radius:3px; background-color:{x};'></span>"
      )
    }
  ) |>
  cols_align(align = "center", columns = fill_color) |>
   cols_align(align = "left", columns = sub_category) |>
  cols_width(fill_color ~ px(24)) |>
  opt_row_striping(row_striping = FALSE) |> 
  tab_options(
    table.border.top.style            = "none",
    table.border.bottom.style         = "none",
    column_labels.border.top.style    = "none",
    column_labels.border.bottom.style = "none",
    data_row.padding                  = px(5)
  )
```

## Column

### Row {height="20%"}

:::{.valuebox .text-white label = "ban_non_inst" icon="clipboard2-pulse-fill" color="#015390"}
Non-Institutional Providers

`r providers$bans[["Non-Institutional"]]`

`r providers$years["Non-Institutional"]`

:::


```{r}
#| label: noninstitutional_providers
#| title: "Non-Institutional Providers"

providers[["df_provider_noninst"]] |> 
  # ggplot(aes(value, fct_reorder(category, value) |> fct_relevel("All Other Providers"))) +
  ggplot(aes(value, category)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(fill = ff_colors$scales$steel[["500"]]) +
  geom_text(
    aes(label = value_fmt),
    hjust = -.1,
    family = "Source Sans 3", color = ff_colors$elements[['annotation']],
    ) +
  scale_x_continuous(expand = c(.005, .005)) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(family = "Source Sans 3", color = ff_colors$elements[["axis"]]),
    axis.text.x = element_blank()
  )
```


## Column

### Row {height=20%} 

:::{.valuebox .text-white label = "ban_DMEPOS" icon="people-fill" color="#015390"}
DMEPOS

`r providers$bans[["DMEPOS"]]`

`r providers$years["DMEPOS"]`

:::


```{r}
#| label: dmepos_viz
#| title: DMEPOS Provider Share

providers[["df_providers_dmepos"]]|> 
  ggplot(aes(share, provider_type, fill = category)) +
  geom_col() +
  scale_fill_manual(values = c(ff_colors$scales$charcoal[["200"]], unname(ff_colors$scales$green[1:4]))) +
  # scale_fill_identity() +
  theme_void() +
  theme(legend.position = "none")

```


```{r}
#| label: dmepos_table
#| title: DMEPOS Provider Table

providers[["df_providers_dmepos_tbl"]] |>
  gt() |> 
  cols_label(
      fill_color = "",
      category = "",
      value = "Count"
    ) |> 
  fmt_number(
    columns = value,
    decimals = 0,
    suffixing = TRUE 
    ) |> 
  text_transform(
    locations = cells_body(columns = fill_color),
    fn = function(x) {
      glue::glue(
        "<span style='display:inline-block; width:14px; height:14px;
         border-radius:3px; background-color:{x};'></span>"
      )
    }
  ) |>
  cols_align(align = "center", columns = fill_color) |>
   cols_align(align = "left", columns = category) |>
  cols_width(fill_color ~ px(24)) |>
  opt_row_striping(row_striping = FALSE) |> 
  tab_options(
    table.border.top.style            = "none",
    table.border.bottom.style         = "none",
    column_labels.border.top.style    = "none",
    column_labels.border.bottom.style = "none",
    data_row.padding                  = px(5)
  )
  
```