---
title: "CMS Fast Facts"
subtitle: "April 2026 Release"
logo: assets/CMS_logo_reverse.png
format: 
  dashboard:
    fig-format: png
    theme:
      - cosmo
      - assets/ff_format.scss
    nav-buttons:
      - icon: github
        href: "#"
        aria-label: "Source Code"
    scrolling: false
knitr:
  opts_chunk: 
    dev: ragg_png
    dpi: 192
resources:
  - assets/CMS_logo_reverse.png
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: dependencies
#| include: false

#dependencies
library(tidyverse)
library(scales, warn.conflicts = FALSE)
library(systemfonts, warn.conflicts = FALSE)
library(patchwork)
library(ggrepel)
library(waffle)
library(gt, warn.conflicts = FALSE)
library(gtExtras)

#add colors

source("Scripts/98_color_system.R")

# Register the OTF font used for pictograms
register_font(
  name  = "FontAwesome7Solid",
  plain = "/Users/c0xu/Library/Fonts/Font Awesome 7 Free-Solid-900.otf"
)

# register_variant(
#   "Source Sans 3 Black",
#   family = "Source Sans 3",
#   weight = "heavy"
# )

```

```{r}
#| label: load_data
#| include: false

#load each dataset needed for each tab, stored in a list element
files <- list.files("Dataout", ".rds") |> str_remove(".rds")
walk(
  files,
  ~ assign(.x, read_rds(paste0("Dataout/", .x, ".rds")), envir = .GlobalEnv)
)
```

# Context

## Row {height="25%"}

:::{.valuebox .text-white  label = "ban_nhe" icon="heart-pulse-fill" color="#4A8C6F"}
National Health Expenditures (NHE)

`r context$bans[["nhe_total"]]`

`r context$years[["nhe_yr"]]`

:::

:::{.valuebox .text-white label = "ban_health-insurance" icon="shield-plus" color="#6E6E6E"}
National Health Insurance Expenditures

`r context$bans[["health_insurance"]]`

`r context$years[["nhe_yr"]]`

:::

:::{.valuebox .text-white label = "ban_fed_spend" icon="bank" color="#015390"}
CMS Federal Program Spending

`r context$bans[["fed_spend"]]`

`r context$years[["fed_spend_yr"]]`

:::

## Row

### Column

#### Row {height="60%"}
```{r}
#| label: share-gdp
#| title: "NHE share of GDP"
#| out-width: 100%
#| fig-height: 4

context[["df_nhe_gdp_share"]] |>
  ggplot() +
  geom_rect(
    aes(
      xmin = 0,
      xmax = 12,
      ymin = 0,
      ymax = 100 / 12
    ),
    color =  "#A6A6A6",
    fill = "white",
    linewidth = 1.1
  ) +
  geom_rect(
    aes(
      xmin = 0,
      xmax = value_sqrt,
      ymin = 0,
      ymax = value_sqrt
    ),
    fill = ff_colors$base[["green"]]
  ) +
  labs(title = context[["df_nhe_gdp_share"]]$value_fmt) +
  coord_equal() +
  theme_void() +
  theme(
    plot.title =
      element_text(
        size = 40, hjust = .5,
        family = "Source Sans 3", face = "bold",
        color = ff_colors$scales$steel["900"]
      ),
    plot.margin = margin(0, 0, 0, 0)
  )


```

#### Row {height="40%"}
```{r}
#| label: per_capita
#| title: "NHE per capita"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

# Value and scale
n_units <- context[["df_nhe_pc"]]$n_icons

icons <- tibble(
  index = 1:(n_units),
  x     = ((index - 1) %% 10) + 1,
  y     = -((index - 1) %/% 10)
)

icons |>
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf0d6",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 30,
    color  = ff_colors$base[["green"]]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(
    title    = context$df_nhe_pc[["value_fmt"]],
    subtitle = "Each icon represents ~$1,000"
  ) +
  theme_void(base_family = "Source Sans 3") +
  theme(
    plot.title    =
      element_text(
        color = ff_colors$scales$steel["900"],
        face = "bold",
        size = 80,
        hjust = 0.5
      ),
    plot.subtitle = element_text(size = 30, hjust = 0.5, color = "gray40"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```

### Column

```{r}
#| label: insurance_bar
#| title: "National Health Insurance Expenditures by Payer"
#| fig-height: 8        
#| out.height: "100%"
#| fig-width: 6

context[["df_insurance"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.3)) +
  geom_col() +
  geom_text(
    aes(label = value_fmt),
    hjust = -.2, size = 6,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_wrap(
    ~fct_reorder(sub_category, value, .desc = TRUE),
    ncol = 1, scales = "free_y"
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    strip.text =
      element_text(
        family = "Source Sans 3 SemiBold",
        color = ff_colors$scales$steel[["900"]],
        size = 20, hjust = 0
      ),
    panel.spacing = unit(0, "lines"),
    panel.grid = element_blank()
  )
```

### Column

#### Row {height="60%"}
```{r}
#| label: fed_spend_pictogram
#| title: "CMS Spending by Category"

context[["df_spend"]] |>
  filter(category == "Federal Program Spending") |>
  ggplot(aes(values = squares, fill = fill_color)) +
  geom_waffle(
    n_rows  = 10,
    size    = 1.5,
    colour  = "white",
    flip    = FALSE
  ) +
  scale_fill_identity() +
  labs(
    subtitle = "Each square represents ~1% of total",
    # caption  = "Source: CMS",
    fill     = NULL
  ) +
  coord_fixed() +
  theme_void() +
  theme(
    plot.title    = element_text(face = "bold", size = 30, hjust = 0.5),
    plot.subtitle = element_text(size = 25, hjust = 0.5, color = "gray40"),
    legend.position = "none"
  )
```


#### Row {height="40%"}
```{r}
#| label: fte
#| title: "CMS Full-Time Equivalents (FTEs)"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

n_units <- context[["fte"]]$n_icons

icons <- tibble(
  x     = 1:(n_units),
  y     = 0
)

icons |>
  ggplot(aes(x = x, y = y)) +
  geom_text(
    label  = "\uf007",              # Font Awesome "person" / user icon
    family = "FontAwesome7Solid",
    size   = 50,
    color  = "#015390" #ff_colors$scales$steel["900"]
  ) +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_y_continuous(expand = expansion(add = 0.5)) +
  labs(
    title    = context$fte[["value_fmt"]],
    subtitle = "Each icon represents ~1,000 FTEs"
  ) +
  theme_void(base_family = "Source Sans 3") +
  theme(
    plot.title =
      element_text(
        size = 80, 
        hjust = .5,
        face = "bold",
        color = ff_colors$scales$steel["900"]
      ),
    plot.subtitle = element_text(size = 30, hjust = 0.5, color = "gray40"),
    plot.caption  = element_text(size = 9, hjust = 0.5, color = "gray60"),
    plot.margin   = margin(10, 10, 10, 10)
  )

```


## Row {.no-title height="5%"}

::: {.footer-source}
`r context[["footnote"]]`
:::


# Beneficiaries


## Row {height="25%"}


:::{.valuebox .text-white label = "ban_medicare_ab" icon="heart-fill" color="#015390"}
Medicare Parts A/B Beneficiaries

`r beneficiaries$bans[["medicare_ab"]]`

`r beneficiaries$years[["medicare"]]`

:::


:::{.valuebox .text-white label = "ban_medicare_d" icon="capsule-pill" color="#015390"}
Medicare Part D Beneficiaries

`r beneficiaries$bans[["medicare_d"]]`

`r beneficiaries$years[["medicare"]]`

:::

:::{.valuebox .text-white label = "ban_medicaid" icon="people-fill" color="#015390"}
Medicaid & CHIP Beneficiaries
 
`r beneficiaries$bans[["medicaid"]]`

`r beneficiaries$years[["medicaid"]]`

:::

## Row

### Column

```{r}
#| label: orig_medicare_utilization
#| title: Medicare Utilization & Spending
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 10

df_background <- beneficiaries[["df_medicare_util"]] |> select(-category)

beneficiaries[["df_medicare_util"]] |>
  ggplot(aes(persons_served, payments, fill = category)) +
  geom_point(
    data = df_background,
    aes(persons_served, payments),
    fill = "grey80", color = "white",
    shape = 21,
    size = 5,
    inherit.aes = FALSE
  ) +
  geom_point(shape = 21, color = "white", size = 7) +
  geom_point(
    data =
      beneficiaries[["df_medicare_util"]] |> filter(sub_category == "Total"),
    shape = 23, color = "white", size = 8
  ) +
  geom_text_repel(
    aes(label = sub_category),
    point.padding = 3,
    box.padding = .5,
    min.segment.length = 0,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    size = 8
  ) +
  facet_wrap(~category) +
  scale_fill_manual(
    values = c(
      ff_colors$scales$cobolt[["200"]],
      ff_colors$scales$cobolt[["700"]],
      ff_colors$scales$cobolt[["900"]]
    )
  ) +
  scale_x_continuous(labels = label_number(scale_cut = cut_short_scale())) +
  scale_y_continuous(
    labels = label_number(prefix = "$", scale_cut = cut_short_scale())
  ) +
  labs(x = "Persons Served", y = "Program Payments", color = "", shape = "") +
  theme_minimal(base_size = 22, base_family = "Source Sans 3") +
  theme(
    panel.spacing = unit(2, "lines"),
    legend.position = "none",
    strip.text =
      element_text(
        color = ff_colors$elements[["title"]],
        face = "bold",
        size = 18
      ),
    axis.title = element_text(face = "bold"),
  )
```

### Column

#### Row
```{r}
#| label: df_medicare_trend
#| title: >-
#|   Medicare Advantage Beneficiaries Now Exceeds
#|    Original Medicare Beneficiaries
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 8

beneficiaries[["df_medicare_trend"]] |>
  ggplot(aes(x = data_year)) +
  geom_blank(aes(y = value_ma * .9)) +
  geom_blank(aes(y = value_orig * 1.3)) +
  geom_ribbon(
    aes(
      ymin = pmin(value_orig, value_ma),
      ymax = pmax(value_orig, value_ma)
    ),
    fill = ff_colors$base["warmgray"], #"lightgray",
    alpha = 0.3
  ) +
  geom_line(aes(y = value_orig, color = "Original Medicare"), linewidth = 2) +
  geom_line(aes(y = value_ma, color = "Medicare Advantage"), linewidth = 2) +
  geom_point(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(
        data_year %in% range(beneficiaries[["df_medicare_trend"]]$data_year)
      ),
    aes(y = value_orig, color = "Original Medicare")
  ) +
  geom_point(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(
        data_year %in% range(beneficiaries[["df_medicare_trend"]]$data_year)
      ),
    aes(y = value_ma, color = "Medicare Advantage")
  ) +
  geom_label(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(data_year == min(data_year)),
    aes(y = value_orig, label = lab_orig, color = "Original Medicare"),
    family = "Source Sans 3", linewidth = NA,
    vjust = -.5, hjust = .6, na.rm = TRUE
  ) +
  geom_label(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(data_year == min(data_year)),
    aes(y = value_ma, label = lab_ma, color = "Medicare Advantage"),
    family = "Source Sans 3", linewidth = NA,
    vjust = 1.1, na.rm = TRUE
  ) +
  geom_label(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(data_year == max(data_year)),
    aes(y = value_orig, label = lab_orig, color = "Original Medicare"),
    family = "Source Sans 3", linewidth = NA,
    vjust = 1, hjust = 0, na.rm = TRUE
  ) +
  geom_label(
    data =
      beneficiaries[["df_medicare_trend"]] |>
      filter(data_year == max(data_year)),
    aes(y = value_ma, label = lab_ma, color = "Medicare Advantage"),
    family = "Source Sans 3", linewidth = NA,
    vjust = -.4, hjust = 0, na.rm = TRUE
  ) +
  geom_label(
    aes(y = value_orig, label = lab_orig_cat, color = "Original Medicare"),
    family = "Source Sans 3", linewidth = NA,
    vjust = -1.5, hjust = 0, na.rm = TRUE
  ) +
  geom_label(
    aes(y = value_ma, label = lab_ma_cat, color = "Medicare Advantage"),
    family = "Source Sans 3", linewidth = NA,
    vjust = 1.5, hjust = 0, na.rm = TRUE
  ) +
  scale_color_manual(
    values =
      c(
        "Original Medicare" = ff_colors$scales$cobolt[["900"]],
        "Medicare Advantage" = ff_colors$scales$cobolt[["200"]]
      )
  ) +
  scale_y_continuous(
    labels = label_number(scale_cut = cut_short_scale()),
    limits = c(0, NA)
  ) +
  scale_x_continuous(
    limits = c(
      min(beneficiaries[["df_medicare_trend"]]$data_year),
      max(beneficiaries[["df_medicare_trend"]]$data_year) + 4
    ),
    breaks = seq(
      from = min(beneficiaries[["df_medicare_trend"]]$data_year),
      to = max(beneficiaries[["df_medicare_trend"]]$data_year),
      by = 5
    )
  ) +
  labs(x = NULL, y = NULL) +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 50) +
  theme(
    legend.position = "none",
    # axis.text.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```


```{r}
#| label: medicaid_exp
#| title: Medicaid Expenditures
#| out-width: 100%
#| out-height: 100%
#| fig-width: 14
#| fig-height: 8

medicaid_exp_tot <- sum(beneficiaries[["df_medicaid_exp"]]$value)

medicaid_exp_tot <-
  label_comma(
    1,
    prefix = "$",
    scale_cut = cut_short_scale()
  )(medicaid_exp_tot)

beneficiaries[["df_medicaid_exp"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value))) +
  geom_blank(aes(x = value * 1.3)) +
  geom_col(fill = ff_colors$base[["teal"]]) +
  geom_text(
    aes(label = value_fmt),
    hjust = -.1, family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    size = 12
  ) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(expand = c(.005, .005)) +
  labs(
    x = NULL, y = NULL,
    title = str_glue("All Services ({medicaid_exp_tot})")
  ) +
  theme_minimal(base_size = 35) +
  theme(
    axis.text.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title =
      element_text(
        face = "bold",
        color = ff_colors$elements[["title"]]
      )
  )
```

#### Row
```{r}
#| label: df_disagg_trend
#| title: "Sub-Populations Trends"
#| out-width: 100%
#| fig-width: 14
#| fig-height: 4

beneficiaries[["df_disagg_trend"]] |>
  ggplot(
    aes(
      data_year, value,
      group = sub_category,
      fill = fill_color, color = fill_color
    )
  ) +
  geom_hline(yintercept = 0, color = ff_colors$elements[["axis"]]) +
  geom_area(alpha = .4) +
  geom_line() +
  geom_point(aes(y = val_pt), na.rm = TRUE) +
  geom_text(
    aes(label = lab_val),
    vjust = -1, na.rm = TRUE,
    family = "Source Sans 3", size = 7,
    color = ff_colors$elements[["annotation"]]
  ) +
  facet_grid(~fct_rev(area) + fct_reorder2(sub_category, data_year, value)) +
  scale_x_continuous(
    breaks =
      range(
        unique(beneficiaries[["df_disagg_trend"]]$data_year),
        na.rm = TRUE
      )
  ) +
  scale_color_identity() +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    legend.position = "none",
    strip.text =
      element_text(
        color = ff_colors$elements[["title"]],
        face = "bold"
      ),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(2.5, "lines")
  )
```



## Row {.no-title height="5%"}

::: {.footer-source}
`r beneficiaries[["footnote"]]`
:::


# Cost Sharing


## Row {height="95%"}
```{r}
#| label: dumbell_charts
#| title: "Medicare Deductibles, Coinsurance, Premiums"

cost_sharing[["df_cs_trend"]]  |>
  ggplot(
    aes(
      value, fct_reorder(sub_category, order, .fun = max, .na_rm = TRUE),
      group = ln_group
    )
  ) +
  geom_path(color = ff_colors$scales$cobolt[["200"]], na.rm = TRUE) +
  geom_point(
    color = "white",
    stroke = 1.1,
    size = 4,
    na.rm = TRUE
  ) +
  geom_point(
    aes(fill = fill_color),
    na.rm = TRUE,
    shape = 21,
    color = ff_colors$base[["azure"]],
    stroke = 1.1,
    size = 4, alpha = .4
  ) +
  geom_text(
    aes(x = mid_pt, label = delta_lab),
    na.rm = TRUE,
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    size = 2.9,
    vjust = -1.1
  ) +
  facet_wrap(~metric_lab, scales = "free", space = "free_y") +
  scale_fill_identity(
    guide = "legend",
    breaks = c("white", ff_colors$scales$cobolt["200"]),
    labels = unique(cost_sharing[["df_cs_trend"]]$period) |> sort()
  ) +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL, fill = NULL) +
  scale_x_continuous(
    label =
      label_number(prefix = "$", scale_cut = cut_short_scale()),
    limits = c(0, NA),
    position = "top"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank(),
    text = element_text(family = "Source Sans 3"),
    strip.text =
      element_text(
        family = "Source Sans 3", face = "bold",
        size = 12, hjust = 0
      ),
    strip.placement = "outside",
    legend.position = "top"
  )

```

## Row {.no-title height="5%"}

::: {.footer-source}
`r cost_sharing[["footnote"]]`
:::

# Providers

## Row {height="25%"}

:::{.valuebox .text-white label = "ban_inst" icon="hospital" color="#015390"}
Medicare Institutional Providers

`r providers$bans[["Institutional"]]`

`r providers$years["Institutional"]`

:::

:::{.valuebox .text-white label = "ban_non_inst" icon="clipboard2-pulse-fill" color="#015390"}
Medicare Non-Institutional Providers

`r providers$bans[["Non-Institutional"]]`

`r providers$years["Non-Institutional"]`

:::

:::{.valuebox .text-white label = "ban_DMEPOS" icon="people-fill" color="#015390"}
Medicare DMEPOS Providers

`r providers$bans[["DMEPOS"]]`

`r providers$years["DMEPOS"]`

:::

## Row

### Column

```{r}
#| label: noninstitutional_providers
#| title: Non-Institutional Provider Types (Counts & Share of Total)
#| out-width: 100%
#| out-height: 100%
#| fig-width: 20
#| fig-height: 20

v_noninst_1 <- providers[["df_provider_noninst"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y =
      element_text(
        # color = ff_colors$elements[["axis"]],
        size = 40
      ),
  )

v_noninst_2 <- providers[["df_provider_noninst"]] |>
  ggplot(aes(share, category, fill = fill_color)) +
  geom_col(aes(x = 1), width = .5, alpha = .2) +
  geom_col(width = .5) +
  geom_text(
    aes(label = share_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(.005, .005)
  ) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank()
  )

v_noninst_1 + v_noninst_2 +
  plot_layout(widths = c(5, 1))

```


### Column

#### Row {height="60%"}
```{r}
#| label: institutional_providers
#| title: Institutional Provider Types (Counts & Share of Total)
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 10

v_inst_1 <- providers[["df_provider_inst"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
  )

v_inst_2 <- providers[["df_provider_inst"]] |>
  ggplot(aes(share, category, fill = fill_color)) +
  geom_col(aes(x = 1), width = .5, alpha = .2) +
  geom_col(width = .5) +
  geom_text(
    aes(label = share_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_fill_identity() +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(.005, .005)
  ) +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank()
  )

v_inst_1 + v_inst_2 +
  plot_layout(widths = c(6, 1))
```


#### Row {height="40%"}

```{r}
#| label: hopsital_type
#| title: "Hospital Provider Subset (Counts & Share of Total)"
#| out-width: 100%
#| out-height: 100%
#| fig-width: 24
#| fig-height: 6

v_hosp_1 <- providers[["df_hospital_subset"]] |>
  ggplot(aes(value, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 45),
  )

v_hosp_2 <- providers[["df_hospital_subset"]] |>
  ggplot(aes(share, fct_reorder(sub_category, value), fill = fill_color)) +
  geom_col(aes(x = 1), width = .5, alpha = .2) +
  geom_col(width = .5) +
  geom_text(
    aes(label = share_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_fill_identity() +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(.005, .005)
  ) +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank()
  )

v_hosp_1 + v_hosp_2 +
  plot_layout(widths = c(7, 1))
```


### Column

```{r}
#| label: dmepos_viz
#| title: DMEPOS Provider Types (Counts & Share of Total)
#| out-width: 100%
#| out-height: 100%
#| fig-width: 20
#| fig-height: 20

v_dmepos_1 <- providers[["df_providers_dmepos"]] |>
  ggplot(aes(value, category, fill = fill_color)) +
  geom_blank(aes(value * 1.1)) +
  geom_col(width = .8) +
  geom_text(
    aes(label = value_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.3
  ) +
  scale_x_continuous(expand = c(.005, .005)) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 40)
  )

v_dmepos_2 <- providers[["df_providers_dmepos"]] |>
  ggplot(aes(share, category, fill = fill_color)) +
  geom_col(aes(x = 1), width = .5, alpha = .2) +
  geom_col(width = .5) +
  geom_text(
    aes(label = share_fmt),
    family = "Source Sans 3",
    color = ff_colors$elements[["annotation"]],
    hjust = -.1
  ) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(.005, .005)
  ) +
  scale_fill_identity() +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_minimal(
    base_size = 35,
    base_family = "Source Sans 3",
  ) +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank()
  )

v_dmepos_1 + v_dmepos_2 +
  plot_layout(widths = c(5, 1))
```

## Row {.no-title height="5%"}

::: {.footer-source}
`r providers[["footnote"]]`
:::
